Trends in the contribution of major causes of death to the black-white life expectancy gap

### 2017-06-02 conferences/Riddell_presentation_max_planck.Rmd
moved conference files

```{r, echo=F}
img1 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/k_morrison.png")), interpolate = FALSE)
img2 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/s_harper2.png")), interpolate = FALSE)
img3 <-  rasterGrob(as.raster(readJPEG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/j_kaufman.jpg")), interpolate = FALSE)
grid.arrange(img3,
             img1,
             img2,
             ncol = 3)
```

@@

```{r, echo = F, out.width = 500}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/Harper_HA_title.png")
```

```{r, echo=F, out.width = 750}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/Harper_HA_fig1.png")
```

@@

```{r, echo = F, out.width = 250}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/Harper_HA_quote.png")
```

@@

```{r, echo = F, out.width = 400}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/alabama.data.ex.png")
```

@@

+ Working paper being screened at bioRxiv
+ R Shiny App: https://corinne-riddell.shinyapps.io/black-white-life-expectancy/

@@

```{r, echo = F, out.width = 800}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/app_ex1.gif")
```

@@

```{r, echo = F, out.width = 800}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/app_ex2.gif")
```

@@

```{r, echo = F, out.width = 800}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/app_ex3.gif")
```

@@

##CVD in men
```{r, echo = F, out.width = 675}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/CVD_men.png")
```

##Cancer in women
```{r, echo = F, out.width = 675}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/Cancer_women.png")
```

##Injury in women
```{r, echo = F, out.width = 675}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/Injury_women.png")
```

>>>>

```{r, echo=F}
img1 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/images/k_morrison.png")), interpolate = FALSE)
img2 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/images/s_harper2.png")), interpolate = FALSE)
img3 <-  rasterGrob(as.raster(readJPEG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/images/j_kaufman.jpg")), interpolate = FALSE)
grid.arrange(img3,
             img1,
             img2,
             ncol = 3)
```

@@

```{r, echo = F, out.width = 500}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/images/Harper_HA_title.png")
```

```{r, echo=F, out.width = 750}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/images/Harper_HA_fig1.png")
```

@@

```{r, echo = F, out.width = 250}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/images/Harper_HA_quote.png")
```

@@

```{r, echo = F, out.width = 400}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/images/alabama.data.ex.png")
```

@@

+ Working paper being screened at bioRxiv
+ R Shiny App: https://corinne-riddell.shinyapps.io/shiny_app/

@@

```{r, echo = F, out.width = 800}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/images/app_ex1.gif")
```

@@

```{r, echo = F, out.width = 800}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/images/app_ex2.gif")
```

@@

```{r, echo = F, out.width = 800}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/images/app_ex3.gif")
```

@@

##CVD in men
```{r, echo = F, out.width = 675}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/images/CVD_men.png")
```

##Cancer in women
```{r, echo = F, out.width = 675}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/images/Cancer_women.png")
```

##Injury in women
```{r, echo = F, out.width = 675}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/images/Injury_women.png")
```
